Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy\\ \thanks{Grantee Capes.}

### 2023-09-30 Text/Articles/MIGARS_2024/migars2024_abstract.tex
Improving LaTeX code

In this paper we consider an estimator based on spacings

This study is dedicated to the analysis of SAR intensity data, which frequently contends with the presence of speckle noise. Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction. In this context, we propose the adoption of the $G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.

@@

\begin{align}
	f(z; \mu, L)=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\}
\end{align}

\begin{align}
	f(z; \alpha, \gamma, L)=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
\end{align}

@@

Vasicek \cite{vasicek1976test}, used $f(x)=p$  to express $ H(f)$ as
\begin{align*}
	H(X)= \int_0^1 \log\left(\frac{d}{dp}Q(p)\right)dp,
\end{align*}

where $Q(p)=F^{-1}(p)=\inf\left\{x: F(x)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.
Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is given by
\begin{align*}
%\label{E:VanEs}
	\widehat{H}_{V}(\bm{X})=\frac{1}{n}&\sum_{i=1}^{n}\log\left\{\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right\},
	\end{align*}
where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $X_{(i)}= X_{(n)}$ if $i>n$.

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by

\begin{align}
%\label{E:VanEs}
	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}&\sum_{i=1}^{n-m}\log\left\{\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right\}.\\
	+&\sum_{k=m}^n\frac{1}{k}+\log\left(\frac{m}{n+1}\right)\nonumber
\end{align}
Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.

>>>>

In this paper we consider an estimator based on spacings.

This study is dedicated to the analysis of SAR intensity data, which frequently contends with the presence of speckle noise. 
Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction. 
We adopt the $\mathcal G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.

@@

\begin{align}
	f(z; \mu, L)&=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\},\\
	f(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
\end{align}

@@

Vasicek \cite{vasicek1976test}, used $f(x)=p$  to express $ H(f)$ as
\begin{equation*}
	H(X)= \int_0^1 \log\left(\frac{d}{dp}Q(p)\right)dp,
\end{equation*}
where $Q(p)=F^{-1}(p)=\inf\left\{x: F(x)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.
Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is given by
\begin{equation*}
%\label{E:VanEs}
	\widehat{H}_{V}(\bm{X})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
	\end{equation*}
where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $X_{(i)}= X_{(n)}$ if $i>n$.

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by
\begin{multline}
%\label{E:VanEs}
	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right]\\
	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
\end{multline}
Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.
